---
title: "data-viz"
author: "Kate Becker"
date: "2024-02-20"
output: html_document
---

library
```{r}
library(tidyverse)
library(streamgraph)
library(viridis)
install.packages("hrbrthemes")
library(hrbrthemes)
library(plotly)
```

data
```{r}
harvest <- read_csv("data/Harvest_All_Sectors.csv")
```

```{r}
harvest <- harvest %>%
  janitor::clean_names()  

commerical <-harvest %>%
  group_by(species) %>%
  filter(sector == "Commercial")
```



```{r}
unique(harvest$sector)
```


```{r}
# Plot
commerical %>% 
  streamgraph(key="species", value="harvest", date="year") %>%
  sg_fill_brewer("BuPu")
```


```{r}
p <- commerical %>% 
  ggplot(aes(x=year, y=harvest, fill=species, text=species)) +
    geom_area(alpha = 0.5) +
    scale_fill_viridis(discrete = TRUE) +
    theme(legend.position="none") +
    ggtitle("Popularity of American names in the previous 30 years") +
    theme(legend.position="none") 
  
ggplotly(p, tooltip="text")

p
```


```{r}
q <- commerical %>% 
  # Compute the proportions:
  group_by(year) %>%
  mutate(freq = harvest/ sum(harvest)) %>%
  ungroup() %>%
  
  # Plot
    ggplot( aes(x=year, y=freq, fill=species, color=species, text=species)) +
    geom_area() +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(legend.position="none") +
    ggtitle("Popularity of American names in the previous 30 years") +
    theme_ipsum() +
    theme(legend.position="none")
ggplotly(q, tooltip="text")
```


```{r}
# Load dataset from github
q <- commerical %>% 
  # Compute the proportions:
  group_by(year) %>%
  mutate(freq = harvest/ sum(harvest)) %>%
  ungroup() %>%
  
  # Plot
    ggplot( aes(x=year, y=harvest, fill=species, color=species, text=species)) +
    geom_area() +
    scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
    theme(legend.position="none") +
    ggtitle("Popularity of American names in the previous 30 years") +
    theme_ipsum() +
    theme(legend.position="none")
ggplotly(q, tooltip="text")

# Plot
commerical %>% 
  streamgraph(key="species", value="harvest", date="year") %>%
  sg_fill_brewer("BuPu")
```


```{r}
p <- data %>% 
  ggplot( aes(x=year, y=n, fill=name, text=name)) +
    geom_area( ) +
    scale_fill_viridis(discrete = TRUE) +
    theme(legend.position="none") +
    ggtitle("Popularity of American names in the previous 30 years") +
    theme_ipsum() +
    theme(legend.position="none") +
ggplotly(p, tooltip="text")


p
```


```{r}
species <- harvest %>%
  filter(sector == "commerical") %>%
  group_by(species) %>%
  mutate(total = sum(harvest)) %>%
  select(harvest, total) %>%
  arrange(desc(total)) %>%
  distinct(species, total) %>%
  head(5)

babynames %>%
  filter(sex == "M", name %in% c("James", "John", "Robert", "Michael", "William")) %>%
  streamgraph("name", "n", "year")
```


```{r}
# Load dataset from github
harvest_stream <- harvest %>% 
  filter(species %in% c("chinook", "chum", "coho",  "pink")) %>%
  filter(sector=="Commerical")

# Plot
harvest_stream %>% 
  streamgraph(key="species", value="harvest", date="year") %>%
  sg_fill_brewer("BuPu")
```


```{r}
install.packages("usmap")
library(usmap)

str(us_map())


df <- us_map(regions = "counties")
AK <- us_map(include = c("AK"))

```


```{r}
# Create data:
#data <- data.frame(
  #year=rep(seq(1990,2016) , each=10),
  #name=rep(letters[1:10] , 27),
  #value=sample( seq(0,1,0.0001) , 270)
#)
 
# Basic stream graph: just give the 3 arguments
pp <- streamgraph(harvest, key="sasap_region", value="harvest", date="year", height="300px", width="1000px")
pp 

# save the widget
# library(htmlwidgets)
saveWidget(pp, file=paste0( getwd(), "/HtmlWidget/streamgraphBasic.html"))


```


```{r}
alaska <- read_csv("data/Alaska-Statewide.csv")

alaska <- alaska %>%
  janitor::clean_names() 
  
```


```{r}
unique(alaska$species_name)
```

```{r}
area_year <- alaska %>%
  group_by(area, year)
```

```{r}
install.packages("plotly")
install.packages("dplyr")
library(plotly)
library(dplyr)

```

```{r}
unique(alaska)
```


```{r}
fig <- alaska %>%
  plot_ly(
  type = "sunburst",
  labels = "area",
  parents = "species_name",
  values = "number_of_fish_estimated"
)
 
fig
```


```{r}
df <- read.csv("https://raw.githubusercontent.com/plotly/datasets/718417069ead87650b90472464c7565dc8c2cb1c/coffee-flavors.csv")

```

```{r}
unique(alaska$area)
```


```{r}
fig <- df |> 
  plot_ly(
    type = "sunburst",
    ids = ~ids,
    labels = ~labels,
    parents = ~parents,
    domain = list(column = 1),
    maxdepth = 2,
    insidetextorientation = "radial"
  )
 
fig
```




```{r}
radarchart(alaska,
           seg = 12,
           title = "Spider",
           pfcol = scales::alpha("gray", 0.3),
           plwd = 2)
```


```{r}
pivot <- alaska %>%
  pivot_wider(names_from = area, values_from = number_of_fish_estimated) %>%
  group_by(year, species_name)
```

```{r}
wide <- alaska %>%
  pivot_wider(names_from = area, values_from = number_of_fish_estimated) 
```


```{r}
unique(pivot)
```


```{r}
islands <- wide %>%
  select(-c(year, species_name, landed_weight_lbs, whole_weight_lbs, permit_count, processor_count, vessel_count)) 
```

```{r}
radarchart(islands,
           seg = 12,
           title = "Spider",
           pfcol = scales::alpha("gray", 0.3),
           plwd = 2)
```


```{r}
library(devtools)
install_github('jokergoo/ComplexHeatmap')
```

```{r}
view(mtcars)
```


```{r}
heat <- alaska %>%
  select(-c(year, area))
```


```{r}
class(hea)
```

```{r}

heat <- heat %>%
  group_by(species_name)
data <- as.matrix(heat) 
```

```{r}
summary(heat)
```

```{r}
view(mtcars)
```

```{r}
catch <- heat %>%
  select(-c(permit_count, vessel_count, processor_count))

```

```{r}
ggplot(catch, )
```


```{r}
heatmap(data, scale = "column")
```

```{r}
class(alaska$year)
```


```{r}
alaska_clean <- alaska |>

  # select cols of interest & update names as needed ----
  select(catch = number_of_fish_estimated, year, species_name) |> 
  
    ggplot(mapping = aes(x = year, y = catch, fill = species_name)) +
  
  # reverse order of groups so level D4 is closest to x-axis ----
  geom_area(position = position_stack(reverse = TRUE)) +
  
  # update colors to match US Drought Monitor (colors selected using ColorPick Eyedropper from original USDM data viz) ----
  scale_fill_manual(values = c("#853904", "#FF0000", "#FFC100", "#FFD965", "#FFFF00")) +
  
  # set x-axis breaks & remove padding between data and x-axis ----
  scale_x_date(breaks = scales::breaks_pretty(n = 10),
               expand = c(0, 0)) +

  # set y-axis breaks & convert values to percentages & & remove padding between data and y-axis----
  scale_y_continuous(breaks = seq(0, 100, by = 10),
                     labels = scales::label_percent(scale = 1),
                     expand = c(0, 0)) 
  
  # add title ----
alaska_clean  

```


```{r}
library(tidyverse)

#..........................import data...........................
tuesdata <- tidytuesdayR::tt_load('2021-07-20')
drought <- tuesdata$drought
```

```{r}
ggplot(alaska, aes(fill = species_name, y = number_of_fish_estimated, x = year)) +
  geom_bar(position = "dodge", stat = "identity")
```

```{r}
library(ggpubr)
library(jpeg)

# Download and read sample image (readJPEG doesn't work with urls)
url <- "https://media.ktoo.org/wp-content/uploads/2023/08/230635_FV_Sallie_wilber-2048x1339-1.jpg"
download.file(url, destfile = "/Users/katebecker/Documents/Bren/Winter/240/final/eds240-visualizations/data/alaska.jpg")
img <- readJPEG("data/alaska.jpg")

ggplot(iris, aes(Species, Sepal.Length)) +
    background_image(img) +
    geom_boxplot(aes(fill = Species))



```
How Have Commercial Salmon Fisheries in Alaska Changed Since 1985?  


```{r}

alaska |> 
  filter(year == 1985) |> 
  slice_max(order_by = number_of_fish_estimated, n = 15) |> 
  ggplot(aes(x = fct_reorder(species_name, number_of_fish_estimated), y = number_of_fish_estimated)) +
  background_image(img) +
  ggalt::geom_lollipop(point.colour = "white") +
  scale_y_continuous(labels = scales::comma, limits = c(0,60000000)) + 
  coord_flip() +
  theme_bw() +
  labs(y = "Catch Numbers", 
       x = "Salmon Species", 
       title = "Commerical Salmon Catches in 1985")


alaska |> 
  filter(year == 2023) |> 
  slice_max(order_by = number_of_fish_estimated, n = 15) |> 
  ggplot(aes(x = fct_reorder(species_name, number_of_fish_estimated), y = number_of_fish_estimated)) +
  background_image(img) +
  ggalt::geom_lollipop(point.colour = "white") +
  scale_y_continuous(labels = scales::comma) + 
  coord_flip() +
  theme_bw() +
  labs(y = "Catch Numbers", 
       x = "Salmon Species", 
       title = "Commerical Salmon Catches in 2023")

par(mfrow = c(2,1))
```

```{r}
alaska |> 
  filter(year == 2023) |> 
  slice_max(order_by = number_of_fish_estimated, n = 15) |> 
  ggplot(aes(x = fct_reorder(species_name, number_of_fish_estimated), y = number_of_fish_estimated)) +
  background_image(img) +
  ggalt::geom_lollipop(point.colour = "white") +
  scale_y_continuous(labels = scales::comma) + 
  coord_flip() +
  theme_bw() +
  labs(y = "Catch Numbers", 
       x = "Salmon Species", 
       title = "2023")

```

```{r}

```


```{r}
alaska |> 
  filter(year == 1985) |> 
  slice_max(order_by = number_of_fish_estimated, n = 15) |> 
  ggplot(aes(x = fct_reorder(species_name, number_of_fish_estimated), y = number_of_fish_estimated)) +
  ggalt::geom_lollipop(point.colour = "white") +
  scale_y_continuous(limits = c(0, )) + 
  coord_flip() +
  theme_bw()
```


```{r}
alaska |> 
  filter(year == 1985) |> 
  slice_max(order_by = number_of_fish_estimated, n = 20) |> 
  ggplot(aes(x = fct_reorder(species_name, number_of_fish_estimated), y = number_of_fish_estimated)) +
  geom_col() +
  geom_text(aes(label = number_of_fish_estimated), size = 4, hjust = 1.5, color = "white") + 
  scale_y_continuous(labels = scales::label_currency(accuracy = 1)) + 
  coord_flip() +
  theme_bw()
  
```


for 240:
- get rid of background 
- 4 data points: box plot to show data distribution
- average and sd dot and error bar or a bar plot 
- use patch work to merge plots together (dumbbell plot)
- background is distracting! too bold ! need. to have a purpsoe, not a fishing vessel question
- include photos at the end of the lolipos (transparent fish) 
- y axis should be in same order 
- dumbbell plot!
- for radar(like melissa) gorup by region 


```{r}
unique(commerical$species)
```


## HW 4

```{r}
# loading the required libraries 
library("jpeg") 
library("ggplot2") 
library("patchwork") 
library(dplyr)

  
# plotting the data 
graph <- ggplot(data_frame, aes(xpos, ypos)) +     
  geom_point() 
  
# specifying the image path 
path <- "/Users/mallikagupta/Desktop/GFG/gfg.jpeg"
  
# read the jpef file from device 
img <- readJPEG(path, native = TRUE) 
  
# adding image to graph  
img_graph <- graph +                   
  inset_element(p = img, 
                left = 0.05, 
                bottom = 0.65, 
                right = 0.5, 
                top = 0.95) 
  
# printing graph with image  
print (img_graph)
```


```{r}

chinook <- "/Users/katebecker/Documents/Bren/Winter/240/final/eds240-visualizations/images/kspencer_chinook.jpg"
coho <- "/Users/katebecker/Documents/Bren/Winter/240/final/eds240-visualizations/images/kspencer_coho.jpg"
sockeye <-"/Users/katebecker/Documents/Bren/Winter/240/final/eds240-visualizations/images/sockeye-salmon.jpg"
pink <- "/Users/katebecker/Documents/Bren/Winter/240/final/eds240-visualizations/images/kspencer_pink.jpg"
chum <- "/Users/katebecker/Documents/Bren/Winter/240/final/eds240-visualizations/images/kspencer_chum.jpg"


salmon_lolli <- alaska |> 
  filter(year == 1985) |> 
  slice_max(order_by = number_of_fish_estimated, n = 15) |> 
  ggplot(aes(x = fct_reorder(species_name, number_of_fish_estimated), y = number_of_fish_estimated)) +
  ggalt::geom_lollipop() +
  scale_y_continuous(labels = scales::comma, limits = c(0,60000000)) + 
  coord_flip() +
  theme_minimal() +
  labs(y = "Catch Numbers", 
       x = "Salmon Species", 
       title = "Commerical Salmon Catches in 1985")

#salmon_lolli +
  #geom_image(aes(x = 0, y = 0, image = chinook_img, size = 0.5))

chinook_img <- readJPEG(chinook, native = TRUE) 
chum_img <-readJPEG(chum, native = TRUE)
sockeye_img <-readJPEG(sockeye, native = TRUE)
coho_img <-readJPEG(coho, native = TRUE)
pink_img <-readJPEG(pink, native = TRUE)


# adding image to graph  
img_graph <- salmon_lolli +                   
  inset_element(p = chinook_img, 
                left = 0.4, 
                bottom = 0.65, 
                right = 0.85, 
                top = 0.5) +
  inset_element(p = chum_img, 
                left = 0.2, 
                bottom = 0.65, 
                right = 0.95, 
                top = 0.5) +
  inset_element(p = sockeye_img, 
                left = 0.4, 
                bottom = 1.2, 
                right = 0.85, 
                top = 1.5) +
  inset_element(p = pink_img, 
                left = 0.4, 
                bottom = 0.65, 
                right = 0.85, 
                top = 0.5) +
  inset_element(p = coho_img, 
                left = 0.4, 
                bottom = 0.65, 
                right = 1.15, 
                top = 0.5) 


# printing graph with image  
print(img_graph)


```
```{r}
names(alaska)
```


```{r}
ggplot(data = alaska, aes(x = year, y = number_of_fish_estimated, colour = species_name)) +
  geom_point() +
  scale_x_continuous()

```

```{r}
ggplot(alaska, aes(x = year, y = number_of_fish_estimated)) +
  geom_density_2d_filled()
```
```{r}
library(stringr)
library(prismatic)
library(Cairo)
library(scales)
library(extrafont)

loadfonts(device = "win")
```
```{r}
```


```{r}
alaska$area <- as.factor(alaska$area)

summary_stats <- alaska %>%
  group_by(area) %>%
  na.omit() %>%
  summarise(mean_fish = mean(number_of_fish_estimated),
            sum_fish = sum(number_of_fish_estimated)) %>%
  mutate(mean_fish= round(mean_fish, digits = 0))

Nrs <- alaska %>%
  group_by(area) %>%
  count()

summary_all <- left_join(summary_stats, Nrs, by = "area")
```


```{r}
#color choice
prismatic::color(c( "#6C5B7B" ,"#C06C84","#F67280","#F8B195"))

#ggplot2
ggplot(summary_all) +
  
  #make custom panel grid
  geom_hline(yintercept = 0, color = "lightgrey") +
  geom_hline(yintercept = 20000000, color = "lightgrey") +
  geom_hline(yintercept = 40000000, color = "lightgrey") +
  geom_hline(yintercept = 60000000, color = "lightgrey") +
  geom_hline(yintercept = 80000000, color = "lightgrey") +
  
  geom_col(aes(
    x = reorder(str_wrap(area,5),sum_fish), #is numeric
    y = sum_fish,#is numeric
    fill = sum_fish), #is a factor
    position = "dodge2",
    show.legend = TRUE,
    alpha = .9) +
      
      #new fill and legend title for number of tracks per region
  scale_fill_gradientn("Fish Sum",
                       colours = c( "#6C5B7B","#C06C84","#F67280","#F8B195"))+
  
  #mean gain per region
  geom_point(aes(x = reorder(str_wrap(area,5),sum_fish),
                 y = mean_fish),
             size = 3,
             color = "gray12")+
  
  #lollipop shaft for mean gain per region
  geom_segment(aes(
    x = reorder(str_wrap(area,5),sum_fish),
    y = 0,
    xend = reorder(str_wrap(area,5),sum_fish),
    yend = 2000000),
    linetype = "dashed",
    color = "gray12") +
  
  coord_polar()
      
```

